Using WordNet and Short-Term Memory for Contextual Disambiguation

### 2016-11-17 Draft_1.tex
Removed irrelevant LaTEX, no need for it in draft
Added subsubsection heading to TFIDF
Added new reference, and began writing NLP section

\documentclass[authoryearcitations]{UoYCSproject}
\author{William T. F. Strachan}
\title{Using WordNet and Short-Term Memory for Contextual Disambiguation}
\date{Literature Review - Draft 1, 10-11-2016}
\supervisor{Dimitar Kazakov}
\MIP
\wordcount{0}

>>>>

\documentclass[twocolumn]{article}
\usepackage{cite}

\begin{document}

\begin{titlepage}
    \begin{center}
        \vspace*{1cm}

        \Huge
        \textbf{Using WordNet and Short-Term Memory for Contextual Disambiguation}
        \vspace{2cm}

        \Large
        \textbf{William T. F. Strachan}

        \vfill

        \vspace{0.8cm}

        \Large
        Word Count - 3000\\
        Supervisor - Dr Dimitar Kazakov\\
        Department of Computer Science\\
        University of York\\
        20 November 2016

    \end{center}
\end{titlepage}

% ------------------------------ START OF DISSERTATION ------------------------------

\section{Literature Review}
\label{sec:LitReview}
In order to define a problem, we must first establish the previous works, so as to build upon them effectively.

\subsection{Natural Language Processing}
\label{sec:NLP}
The problem of natural language processing or, more specifically, input text analysis, has traditionally be broken down into smaller sub-problems\cite{NLPHandbook}:
\begin{itemize}
	\item Text Preprocessing
	\item Lexical Analysis
	\item Syntactic Parsing
	\item Semantic Analysis
\end{itemize}
The subsequent subsections will discuss each of these in more detail.

\subsubsection{Text Preprocessing}
\label{sec:TextPreprocessing}
Before any analysis can take place, the inputted raw text must be converted into a usable format. This, once again, can be broken down into multiple steps\cite{NLPHandbook}: 
\begin{itemize}
	\item Character encoding must be identified
	\item The language can then be identified. Language is most commonly found using one of two methods: Language can be identified by character set, in cases where language uses a unique alphabet, or by character frequency, in other cases.
	\item Non-useful data, such as images and html formatting must be removed.
\end{itemize}

\subsubsection{Lexical Analysis}
\label{sec:LexicalAnalysis}

\subsubsection{Syntactic Parsing}
\label{sec:SyntacticParsing}

\subsubsection{Semantic Analysis}
\label{sec:SemanticAnalysis}

\bibliography{references}
\bibliographystyle{IEEEtran}

\end{document}
